Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification

### 2021-04-07 template.tex
normalize H

\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\include{snippets}

\newtheorem{theorem}{Theorem}

\begin{document}
\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
\author{Chenran Lin \and Lok-Ming Lui}
\date{}

@@

\begin{abstract}
    There is a growing interest in shape analysis in recent years and in this paper we present a novel contour-based shape representation named Beltrami signature for 2D bounded simple connected domain. The proposed representation is based on conformal welding. With suitable normalization, the uniqueness of welding is guaranteed up to a rotation. Then it can be extended to a harmonic function and finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension. The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion. Experiments demonstrates the above properties and also shows the excellent classification performance.
\end{abstract}

\keywords{Shape representation, conformal welding, simple connected,invariance}

\section{Introduction}
    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on. However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like. Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information. Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.

@@

    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature. Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points. Under suitable normalization, conformal welding $f: \partial \D \rightarrow \partial \D$ can be determined up to a rotation. Such conformal welding can be extended to the whole unit disk and get a harmonic function $F: \D \rightarrow \D$ and the Beltrami coefficient of $F$ is our Beltrami signature.

@@

    \begin{figure}
        \begin{center}
        \includegraphics[width=\textwidth]{src/fig1.png}
        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
        \end{center}
        \label{fig1}
    \end{figure}

\section{Theoretical basis}\label{background}
    \subsection{Quasi-conformal mapping and Beltrami equation}
        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
        \[
            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
        \]

        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
        \begin{equation}\label{beltrami eq}
            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
        \end{equation}
        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$. More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
        \begin{equation}
            \mu = \frac{f_{\overline{z}}}{f_{z}}
        \end{equation}
        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
        \begin{equation}
            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
        \end{equation}
        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$. $\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality. In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$. Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
        \begin{equation}\label{local f}
            f(z) = f(p)+f_z(p)z+f_{\overline{z}}(p)\overline{z} = f(p)+f_z(p)(z+\mu(p)\overline{z}).
        \end{equation}

        \begin{figure}
            \begin{center}
                \includegraphics[width=8cm]{src/fig2.jpg}
            \end{center}
            \caption{(a) Shows the original hippocampus. (b) Shows the parameter domain with circle packing pattern. Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
            \label{fig2}
        \end{figure}

@@

        \begin{figure}
            \begin{center}
                \includegraphics[width=8cm]{src/fig3.jpg}
            \end{center}
            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
            \label{fig3}
        \end{figure}

@@

    % \subsection{Reconstruction from conformal welding}
    %     Another important thing is that how we reconstruct the original domain $\Omega$ when we know the shape signature $f: \partial \D \rightarrow \partial \D$. Firstly, we can define $F: \D \rightarrow \D$ as
    %     \begin{equation}
    %         F(re^{i\theta}) = rf(e^{i \theta}) = r \Phi_1^{-1} \circ \Phi_2(e^{i\theta}),
    %     \end{equation}
    %     then we define
    %     \begin{equation}
    %         G(z) = \begin{cases}
    %             \Phi_1 \circ F, & z \in \D\\
    %             \Phi_2, & z \notin \D
    %         \end{cases}.
    %     \end{equation}
    %     It is easy to check such a $G$ is well-defined. For all $z \in \partial \D$, 
    %     $$\Phi_1 \circ F(z) = \Phi_1 \circ \Phi_1^{-1} \circ \Phi_2(z) = \Phi_2(z).$$
    %     Now we consider the Beltrami coefficient of G
    %     \begin{equation}\label{PDE reconstruct conformal welding}
    %         \mu_G = \frac{G_{\overline{z}}}{G_z} = \begin{cases}
    %             \mu_{\Phi_1 \circ F} = \mu_F,& z \in \D\\
    %             \mu_{\Phi_2} = 0, & z \notin \D
    %         \end{cases},
    %     \end{equation}
    %     and the map $G$ is the solution of above PDE (\ref{PDE reconstruct conformal welding}), which can be solved out by LBS method. Therefore, $\Phi_1 = G|_\D \circ F^{-1}$, $\Phi_2 = G|_{\D^c}$ and $\Omega = G \circ F^{-1}(\D)$ or $\Omega = G(\D^c)^c$.
    \subsection{Harmonic function and Poisson integral}
        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
        \begin{equation}
            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
        \end{equation}
        where $z = x + iy$, $x$, $y$ is the real and imaginary value.

@@

        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}. For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $F : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
            \begin{equation}\label{poisson integral}
                F(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
            \end{equation}
        Such $F$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e. $F(e^{i\theta}) = f(e^{i\theta})$ (see Fig. \ref{harmonic}). Of course, this $F$ is unique.

        \begin{figure}
            \begin{center}
                \includegraphics[width=\textwidth]{src/fig4.png}
            \end{center}
            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$. (b) The corresponding harmonic function $F$ generated from $f$ by the equation (\ref{poisson integral}). Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
            \label{harmonic}
        \end{figure}

    \section{Beltrami signature}\label{main}
        In this chapter, we will propose a new signature, Beltrami signature, to representation boundary simple connected domain $\Omega$. Our proposed signature is based on conformal welding. But with some normalization.

        \subsection{Beltrami signature based on conformal welding}
            Here we give a brief explaination of how to create our new signature. Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it. Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $f$ is determined up to a rotation. Then $f$ can be extended to harmonic function $F$ defined on $\D$ by Poisson integral. At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
            \begin{equation}
                B:= \mu_F = \frac{F_{\overline{z}}}{F_z}.
            \end{equation}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig5.png}
                \end{center}
                \caption{Illustration of Beltrami signature. (a) The input shape, a dolphin. (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b). (c) The Beltrami signature of original shape. Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                \label{illu of BS}
            \end{figure}

@@

            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{F}$. The following theorem show the relationship between $F$ and $\tilde{F}$.

            \begin{theorem}
                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations. $F$ and $\tilde{F}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{F} = M_1^{-1} \circ F \circ M_2$ iff $M_1$ is a rotation.
            \end{theorem}

@@

                $\Rightarrow :$ When $\tilde{F} = M_1^{-1} \circ F \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $F \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal. $\tilde{F}$ and $F \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$. Therefore, we have $$e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,$$ which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.

                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ F \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}. It's easy to check that
                \[
                    M_1^{-1} \circ F \circ M_2 (e^{i \theta}) = M_1^{-1} \circ f \circ M_2(e^{i \theta}) = \tilde{f}(e^{i \theta}) = \tilde{F} (e^{i \theta}),
                \]
                which means $M_1^{-1} \circ F \circ M_2$ and $\tilde{F}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ F \circ M_2 = \tilde{F}$.
            \end{proof}

            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{F}$
            \begin{equation}
                \tilde{B} = \mu_{\tilde{F}} = \mu_{M_1^{-1} \circ F \circ M_2} = \mu_{F \circ M_2}.
            \end{equation}
            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{F \circ M_2} = \mu_{F} = B$, then we get $M_2$ is identity. Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
            \begin{enumerate}
                \item $\Phi_1: \D \rightarrow \Omega$ should be determined up to a rotation.
                \item $\Phi_2: \D^c \rightarrow \Omega^c$ should be uniquely determined.
            \end{enumerate}

        \subsection{Normalization to $\Phi_1$}\label{norm1}
            We hope $\Phi_1$ is determined up to a rotation. It is not that hard, for example, we can normalize $\Phi_1$ by restricting $\Phi_1(0) = 0$. But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold. Here we want to show a new approach which can determine $\Phi_1$ up to a rotation without any additional assumption.

            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n$ of $\Omega$. Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, we claims that $\Phi_1$ can be normalized by restricting the center of $p_i$ to $0$.

            \begin{theorem}\label{unique up to a rotation}
                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
                \begin{align}\label{norm phi1}
                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
                \end{align}
                then such $\Phi_1$ is unique up to a rotation.
            \end{theorem}

@@

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig6.png}
                \end{center}
                \caption{The first row are some randomly generated points in $\partial \D$. The second row are the corresponding $\abs{f(a)}$, where $a \in \D$. The third row are also $\abs{f(a)}$ but is in top view. }
                \label{fasolvable}
            \end{figure}

@@

            \begin{proof}
                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
                \begin{equation*}
                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
                \end{equation*}
                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
                $$g(a) = \begin{cases}
                \frac{1}{n} f(a) + a, a \in \D,\\
                0, a \in \partial \D,
                \end{cases}
                $$
                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.

                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
                $$
                h(a) = \begin{cases}
                    g(a), &a \in  \overline{\D} \setminus M,\\
                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
                \end{cases}
                $$
                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.

@@

                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$. For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
                \begin{equation*}
                    F_a(p_k) = F_a(\cos \theta_k + \sin \theta_k i) = \frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} = \frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
                \end{equation*}
                so
                \begin{equation*}
                    \Re(F_a(p_k)) = \frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} = \cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} < \cos \theta_k = \Re(p_k).
                \end{equation*}

                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
                \begin{equation*}
                    \Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) < \sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
                \end{equation*}
                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
            \end{proof}

            In the fact, no matter how these $p_i$ distribute, we can reduce it to the special mentioned above.

>>>>

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
% \smartqed  % flush right qed marks, e.g. at end of proof
%
% \let\equation\relax
% \let\endequation\relax
\let\proof\relax
\let\endproof\relax
\let\example\relax
\let\endexample\relax

\usepackage{graphicx}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\include{snippets}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Chenran Lin \and Lok Ming Lui}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Chenran Lin \at
              Department of Mathematics, The Chinese University of Hong Kong \\
              \email{crlin@math.cuhk.edu.hk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Lok Ming Lui \at
              Department of Mathematics, The Chinese University of Hong Kong\\
              \email{lmlui@math.cuhk.edu.hk}           %  \\
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature. The proposed signature is based on conformal welding. We extended the welding mapping to a harmonic function. With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation. And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.  The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion. Experiments demonstrate the above properties and also show the excellent classification performance.
\keywords{
  Shape representation \and conformal welding \and simple connected \and invariance}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on. However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like. Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information. Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.

@@

    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature. Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.  Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$. Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.

@@

    \begin{figure}
        \begin{center}
        \includegraphics[width=7.6cm]{src/fig1_down.png}
        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
        \end{center}
        \label{fig1}
    \end{figure}

\section{Theoretical basis}\label{background}
    \subsection{Quasi-conformal mapping and Beltrami equation}
        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
        \begin{equation*}
            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
        \end{equation*}

        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
        \begin{equation}\label{beltrami eq}
            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
        \end{equation}
        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$. More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
        \begin{equation}
            \mu = \frac{f_{\overline{z}}}{f_{z}}
        \end{equation}
        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
        \begin{equation}
            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
        \end{equation}
        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$. $\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality. In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$. Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
        \begin{equation}\label{local f}
            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
        \end{equation}

        \begin{figure}
            \begin{center}
                \includegraphics[width=7.6cm]{src/fig2.jpg}
            \end{center}
            \caption{(a) Shows the original hippocampus. (b) Shows the parameter domain with circle packing pattern. Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
            \label{fig2}
        \end{figure}

@@

        \begin{figure}
            \begin{center}
                \includegraphics[width=7.6cm]{src/fig3.jpg}
            \end{center}
            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
            \label{fig3}
        \end{figure}

@@

    \subsection{Harmonic function and Poisson integral}
        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
        \begin{equation}
            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
        \end{equation}
        where $z = x + iy$, $x$, $y$ is the real and imaginary value.

@@

        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}. For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
            \begin{equation}\label{poisson integral}
                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
            \end{equation}
        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e. $H(e^{i\theta}) = f(e^{i\theta})$ (see Fig. \ref{harmonic}). Of course, this $H$ is unique.

        \begin{figure}
            \begin{center}
                \includegraphics[width=7.6cm]{src/fig4_down.png}
            \end{center}
            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$. (b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}). Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
            \label{harmonic}
        \end{figure}

    \section{Beltrami signature}\label{main}
        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$. Our proposed signature is based on conformal welding and quasi-conformal theory.

        \subsection{Beltrami signature based on conformal welding}
            Here we give a brief explaination of how to create our new signature. Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it. Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}). At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
            \begin{equation}
                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
            \end{equation}
            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.

            \begin{figure*}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig5.png}
                \end{center}
                \caption{Illustration of Beltrami signature. (a) The input shape, a dolphin. (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b). (c) The Beltrami signature of (a). Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                \label{illu of BS}
            \end{figure*}

@@

            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.

            \begin{theorem}
                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations. $H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
            \end{theorem}

@@

                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal. $\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$. Therefore, we have 
                \begin{equation*}
                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
                \end{equation*}
                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.

                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}. It's easy to check that
                \begin{align*}
                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
                \end{align*}
                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
            \end{proof}

            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
            \begin{equation}
                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
            \end{equation}
            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity. Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
            \begin{enumerate}
                \item $M_1$ should be a rotation.
                \item $M_2$ should be identity.
            \end{enumerate}

        \subsection{Normalization to $M_1$}\label{norm1}
            We hope $M_1$ is a rotation. It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$. But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold. Here we want to show a new approach without any additional assumption.

            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$. Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$. We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.

            \begin{theorem}\label{unique up to a rotation}
                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
                \begin{align}\label{norm phi1}
                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
                \end{align}
                then such $\Phi_1$ is unique up to a rotation $M_1$.
            \end{theorem}

@@

            \begin{figure*}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig6.png}
                \end{center}
                \caption{The first row are some randomly generated points in $\partial \D$. The second row are the corresponding $\abs{f(a)}$, where $a \in \D$. The third row are also $\abs{f(a)}$ but is in top view. }
                \label{fasolvable}
            \end{figure*}

@@

            \begin{proof}
                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
                \begin{equation*}
                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
                \end{equation*}
                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
                \begin{equation*}
                    g(a) = \begin{cases}
                \frac{1}{n} f(a) + a, a \in \D,\\
                0, a \in \partial \D,
                \end{cases}
                \end{equation*}
                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.

                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
                \begin{equation*}
                    h(a) = \begin{cases}
                    g(a), &a \in  \overline{\D} \setminus M,\\
                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
                \end{cases}
                \end{equation*}
                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.

@@

                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$. For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
                \begin{align*}
                    &F_a(p_k) \\
                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
                \end{align*}
                so
                \begin{align*}
                    &\Re(F_a(p_k)) \\
                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
                    < &\cos \theta_k = \Re(p_k).
                \end{align*}

                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
                \begin{align*}
                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
                \end{align*}
                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
            \end{proof}

            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
